---
title: "ToM iPad"
author: "Kimberly A. Brink"
date: "March 25, 2016"
output: html_document
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(echo=TRUE, warning=FALSE, message=FALSE, fig.width=16)
```

```{r install_libraries}
library(lubridate)
library(Hmisc)
```

```{r standard_error}
s.error <- function(x) sd(x)/sqrt(length(x))
```

```{r load_file}
filename="/Volumes/lsa-research01/ALL STUDIES/Current Studies/ToM iPad/ToM iPad.sav"
ToM <- spss.get(filename,datevars=c("DOB","DOT"))
```

```{r calculate_variables}
ToM$Age = (year(as.period(interval(ToM$DOB, ToM$DOT)))*12) + month(as.period(interval(ToM$DOB, ToM$DOT))) + (day(as.period(interval(ToM$DOB, ToM$DOT)))/30)
ToM$AgeYears = ToM$Age/12
```

###Demographics.
There were `r length(ToM$SubID)` participants.

The average age of participants was `r round(mean(ToM$Age)/12,2)` years old.

The oldest participant was `r round(max(ToM$Age)/12,2)` years old.

The youngest participant was `r round(min(ToM$Age)/12,2)` years old.

There were `r dim(ToM[which(ToM$AgeYears>6),])[1]` participants older than 6`

There were `r dim(ToM[which(ToM$AgeYears<=6),])[1]` participants younger than 6`


```{r hist_age}
agehist = hist(ToM$AgeYears, breaks = 20, col = ifelse(ToM$AgeYears<=6,'red','blue'))
text(agehist$counts)
```

```{r compute_scores}
ToM$DD.score = ifelse(ToM$DD1!=ToM$DD2,1,0) 
ToM$DB.score = ifelse(ToM$DB1!=ToM$DB2,1,0)
ToM$KA.score = ifelse(ToM$KA3=="No"&ToM$KA4=="No",1,0)
ToM$CFB.score = ifelse(ToM$CFB3=="Band-aids"&ToM$CFB4=="No",1,0)
ToM$HE.score = ifelse((ToM$HE3=="Sad"&ToM$HE4=="Happy"&ToM$HE5cor==1)|(ToM$HE3=="Sad"&ToM$HE4=="OK"&ToM$HE5cor==1)|(ToM$HE3=="OK"&ToM$HE4=="Happy"&ToM$HE5cor==1),1,0)
ToM$scale.score = ToM$DD.score + ToM$DB.score + ToM$KA.score + ToM$CFB.score + ToM$HE.score
#Professional voices.

ToM = ToM[ToM$SubID > 12,]

```

```{r}
ToM.scale = ToM[,c('DD.score','DB.score','KA.score','CFB.score','HE.score')]
apply(ToM.scale, 2, mean, na.rm=T)

plot(ToM$Age,ToM$scale.score)
cor.test(ToM$Age,ToM$scale.score)
```

```{r mixRasch}
#pretty much only gives me results for one type of rasch model
#gives results for rasch table
library(mixRasch)
mr.mod = mixRasch(ToM.scale, steps = 1, max.iter = 1000000, conv.crit = 0.00001, model = "PCM", n.c = 1)
mr.mod
```

```{r guttman_analysis}
#perform guttman analysis (by hand)
library(sirt)

gutt.mod = prob.guttman(ToM.scale)
summary(gutt.mod)

#green's coefficient of reproducibility (1956)

#sum the number respondents with positive responses for each item
apply(ToM.scale, 2, sum, na.rm=T)

#sum the number of respondents who got g correct
g_11 = sum(ToM.scale$DD.score,na.rm=T)
g_12 = sum(ToM.scale$DB.score,na.rm=T)
g_13 = sum(ToM.scale$KA.score,na.rm=T)
g_14 = sum(ToM.scale$CFB.score,na.rm=T)
g_15 = sum(ToM.scale$HE.score,na.rm=T)

#sum the number of respondents who got g incorrect
g_01 = sum(ifelse(ToM.scale$DD.score==0,1,0),na.rm=T)
g_02 = sum(ifelse(ToM.scale$DB.score==0,1,0),na.rm=T)
g_03 = sum(ifelse(ToM.scale$KA.score==0,1,0),na.rm=T)
g_04 = sum(ifelse(ToM.scale$CFB.score==0,1,0),na.rm=T)
g_05 = sum(ifelse(ToM.scale$HE.score==0,1,0),na.rm=T)

#sum the number of respondents who got item g+1 correct and g incorrect, where g = 1,...,k-1
g_12_01 = sum(ifelse(ToM.scale$DB.score==1&ToM.scale$DD.score==0,1,0),na.rm=T)
g_13_02 = sum(ifelse(ToM.scale$KA.score==1&ToM.scale$DB.score==0,1,0),na.rm=T)
g_14_03 = sum(ifelse(ToM.scale$CFB.score==1&ToM.scale$KA.score==0,1,0),na.rm=T)
g_15_04 = sum(ifelse(ToM.scale$HE.score==1&ToM.scale$CFB.score==0,1,0),na.rm=T)

#sum the number of respondents who got items g+2 and g+1 correct and items g and g-1 incorrect
g_143_021 = sum(ifelse(ToM.scale$CFB.score==1&ToM.scale$KA.score==1&ToM.scale$DB.score==0&ToM.scale$DD.score==0,1,0),na.rm=T)
g_154_032 = sum(ifelse(ToM.scale$HE.score==1&ToM.scale$CFB.score==1&ToM.scale$KA.score==0&ToM.scale$DB.score==0,1,0),na.rm=T)

#sum the number of respondents who got item g+2 correct and g incorrect, where g = 2,...,k-2
g_13_01 = sum(ifelse(ToM.scale$KA.score==1&ToM.scale$DD.score==0,1,0),na.rm=T)
g_14_02 = sum(ifelse(ToM.scale$CFB.score==1&ToM.scale$DB.score==0,1,0),na.rm=T)
g_15_03 = sum(ifelse(ToM.scale$HE.score==1&ToM.scale$KA.score==0,1,0),na.rm=T)

Rep_A = 1 - (1/(dim(ToM.scale)[1]*dim(ToM.scale)[2]))*(g_12_01+g_13_02+g_14_03+g_15_04) - (1/(dim(ToM.scale)[1]*dim(ToM.scale)[2]))*(g_143_021*g_154_032)

Rep_B = 1 - (1/(dim(ToM.scale)[1]*dim(ToM.scale)[2]))*(g_12_01+g_13_02+g_14_03+g_15_04) - (1/((dim(ToM.scale)[1]^2)*dim(ToM.scale)[2]))*((g_14_02*g_13_01)+(g_15_03*g_14_02))

se.Rep_A = sqrt(((1-Rep_A)*(Rep_A))/(dim(ToM.scale)[1]*dim(ToM.scale)[2]))
se.Rep_B = sqrt(((1-Rep_B)*(Rep_B))/(dim(ToM.scale)[1]*dim(ToM.scale)[2]))

#green's index of consistency

Rep_I = 1 - (1/((dim(ToM.scale)[1]^2)*dim(ToM.scale)[2]))*((g_12*g_01)+(g_13*g_02)+(g_14*g_03)+(g_15*g_04)) - (1/((dim(ToM.scale)[1]^4)*dim(ToM.scale)[2]))*((g_14*g_13*g_02*g_01)+(g_15*g_14*g_03*g_02))

I_A = (Rep_B-Rep_I)/(1-Rep_I)
I_B = (Rep_A-Rep_I)/(1-Rep_I)

#green's coefficient of reproducibility (1956)
Rep_A
Rep_B

#green's coefficient of reproducibility (1956) by chance
Rep_I

#green's index of consistency, should be greater than .5
I_A
I_B
```

