---
title: "ToM iPad"
author: "Kimberly A. Brink"
date: "March 25, 2016"
output: html_document
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(echo=TRUE, warning=FALSE, message=FALSE, fig.width=16)
```

```{r install_libraries}
library(lubridate)
library(Hmisc)
```

```{r standard_error}
s.error <- function(x) sd(x)/sqrt(length(x))
```

```{r load_file}
filename="/Volumes/lsa-research01/ALL STUDIES/Current Studies/ToM iPad/ToM iPad.sav"
ToM <- spss.get(filename,datevars=c("DOB","DOT"))
```

```{r calculate_variables}
ToM$Age = (year(as.period(interval(ToM$DOB, ToM$DOT)))*12) + month(as.period(interval(ToM$DOB, ToM$DOT))) + (day(as.period(interval(ToM$DOB, ToM$DOT)))/30)
ToM$AgeYears = ToM$Age/12
```

###Demographics.
There were `r length(ToM$SubID)` participants.

The average age of participants was `r round(mean(ToM$Age)/12,2)` years old.

The oldest participant was `r round(max(ToM$Age)/12,2)` years old.

The youngest participant was `r round(min(ToM$Age)/12,2)` years old.

There were `r dim(ToM[which(ToM$AgeYears>6),])[1]` participants older than 6`

There were `r dim(ToM[which(ToM$AgeYears<=6),])[1]` participants younger than 6`


```{r hist_age}
agehist = hist(ToM$AgeYears, breaks = 20, col = ifelse(ToM$AgeYears<=6,'red','blue'))
text(agehist$counts)
```

```{r compute_scores}
ToM$DD.score = ifelse(ToM$DD1!=ToM$DD2,1,0) 
ToM$DB.score = ifelse(ToM$DB1!=ToM$DB2,1,0)
ToM$KA.score = ifelse(ToM$KA3=="No"&ToM$KA4=="No",1,0)
ToM$CFB.score = ifelse(ToM$CFB3=="Band-aids"&ToM$CFB4=="No",1,0)
ToM$HE.score = ifelse((ToM$HE3=="Sad"&ToM$HE4=="Happy")|(ToM$HE3=="Sad"&ToM$HE4=="OK")|(ToM$HE3=="OK"&ToM$HE4=="Happy"),1,0)
ToM$scale.score = ToM$DD.score + ToM$DB.score + ToM$KA.score + ToM$CFB.score + ToM$HE.score
#Professional voices.

ToM = ToM[ToM$SubID > 12,]

```

```{r}
mean(ToM$DD.score,na.rm=T)
mean(ToM$DB.score,na.rm=T)
mean(ToM$KA.score,na.rm=T)
mean(ToM$CFB.score,na.rm=T)
mean(ToM$HE.score,na.rm=T)
plot(ToM$Age,ToM$scale.score)
cor.test(ToM$Age,ToM$scale.score)

ToM.scale = ToM[,c('DD.score','DB.score','KA.score','CFB.score','HE.score')]
apply(ToM.scale, 2, mean, na.rm=T)
```

```{r IITA}

library(DAKS)
ToM.scale = ToM[,c('DD.score','DB.score','KA.score','CFB.score','HE.score')]
ToM.scale = ToM.scale[complete.cases(ToM.scale),]

#10 largest response patterns in the data:
pat = pattern(ToM.scale)
pat
sum(pat$response.patterns)
sum(pat$response.patterns)/length(ToM.scale$DD.score)

apply(ToM.scale, 2, table)[2,]

mini <- iita(ToM.scale, v = 1)
corr <- iita(ToM.scale, v = 2)
orig <- iita(ToM.scale, v = 3)

summary(mini)
summary(corr)
summary(orig)

#We additionally present the inductively generated selection set of competing quasi orders, because that helps investigating the results obtained from applying the IITA algorithms
sel_set <- ind_gen(ob_counter(ToM.scale))
sel_set
```

```{r mRm}
#I'm pretty sure this is what we want to do to identify multiple rasch models, but I get weird results
library(mRm)
mrm.mod = mrm(ToM.scale, cl=1, max.it = 10000, conv.crit = .0001)
summary(mrm.mod)
plot(mrm.mod)
```

